\Title

### 2021-01-25 manuscript/manuscript.tex

In the following sections, we will test the effectiveness and trade-offs of
each of these strategies on synthetic data.

\section{Tests on synthetic data}

We have used synthetic gravity datasets to test the interpolation accuracy of
the difference horizontal and vertical source distribution strategies as well
as the gradient-boosted equivalent source method.
To generate the data, we created a model that is made out of \NPrisms{}
right-rectangular prisms, distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
\ModelDepth{} and zero.
The density contrast of prisms ranges from \ModelMinDensity{} to
\ModelMaxDensity{}.
The model includes prisms of different shapes, sizes, and depths to create
gravity disturbances with a variety of wavelengths.

We created two synthetic datasets from the model, one simulating a ground
survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
To create the synthetic ground survey, we selected measurement positions from a
portion of a public domain dataset for Southern Africa, available through the
NOAA National Centers for Environmental Information (NCEI)\footnote{
\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
(last accessed 25 January 2020)}.
For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
Ltd between 1955 and 1965 and made publicly available by the
British Geological Survey (BGS)\footnote{
\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
(last accessed 25 January 2020)}.
In both cases, we rescaled the horizontal coordinates of each survey portion to
span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
dimensions.
The ground survey contains \GroundSurveyPoints{} observations distributed at
heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}a).
The airborne survey has \AirborneSurveyPoints{} observations at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-layouts}c).

The vertical component of the gravitational acceleration generated by the
model was computed  using the method of \citet{nagy2000, nagy2002}
with recent modifications by \citet{fukushima2020},
as implemented in the open-source software Harmonica \citep{harmonica}.
We generated a \emph{target grid} of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} and located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
interpolation error.
We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
deviation.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
    \caption{
        Maps of the observation locations and gravity values for the synthetic
        ground and airborne surveys.
        (a)~Horizontal position and height of the ground survey points.
        (b)~Synthetic gravity data calculated on the ground survey points with
        added pseudo-random Gaussian noise.
        (c)~Horizontal position and height of the airborne survey points.
        (d)~Synthetic gravity data calculated on the airborne survey points
        with added pseudo-random Gaussian noise.
        Heights are given in meters above the zero height plane.
    }
    \label{fig:synthetic-layouts}
\end{figure*}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Pseudo-color map of the target grid of synthetic gravity data. The grid
        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
        above the zero height plane.
    }
    \label{fig:synthetic-target}
\end{figure}

\subsection{Comparison of source distribution strategies}

@@

@@

@@

\subsection{Performance and accuracy of gradient boosting}

@@

\subsubsection{Window size}
\label{sec:window_size}

@@

\subsubsection{Amount of overlap}

@@

Finally, the equivalent sources are used to predict the values of the gravity
disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid
(see Fig.~\ref{fig:australia-grid}).

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-grid.png}
    \caption{
        Interpolated gravity disturbance of Australia on a regular grid at
        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
        were obtained through gradient-boosted equivalent sources.
    }
    \label{fig:australia-grid}
\end{figure*}

@@

\section{Discussion}

\subsection{Location of sources}

>>>>

In the following sections, we will test the effectiveness and trade-offs of
each of these strategies on synthetic data.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comparison of source distributions}

@@

\subsection{Synthetic Model}

%Describe forward model made out of prisms.
%Show prisms model?

The synthetic model is made out of \NPrisms{} prisms distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
height plane.
Density contrast of prisms range from \ModelMinDensity{} and
\ModelMaxDensity{}.
We built deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:target-grid}), using \citet{nagy2000} and \citet{nagy2002}.
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
        zero height plane.
    }
    \label{fig:target-grid}
\end{figure}

\subsection{Synthetic Surveys}

In order to compare the predictive capabilities of each source distribution
under on different surveys, we created a ground and an airborne \emph{synthetic
surveys}.
For creating the synthetic ground survey we selected a portion of the Southern
Africa Gravity Data available through the
\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
For the airborne survey we used a portion of the Great Britain Aeromagnetic
Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
Ltd between 1955 and 1965 and made available by the
\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
British Geological Survey (BGS)
}.

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
The ground survey is composed by \GroundSurveyPoints{} observation points
distributed at heights ranging between \GroundSurveyMinHeight{} and
\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has \AirborneSurveyPoints{} points at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the ground survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
    \caption{
        Synthetic airborne survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
        Based upon the Great Britain aeromagnetic data, with the permission of
        the British Geological Survey.
    }
    \label{fig:synthetic-airborne-survey}
\end{figure}

\subsection{Comparisons}

@@

\subsection{Discussion}

@@

\section{Performance of gradient-boosted equivalent sources}

@@

\subsection{Window size}
\label{sec:window_size}

@@

\subsection{Amount of overlap}

@@

Finally, the equivalent sources are used to predict the values of the gravity
disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid
(Fig.~\ref{fig:australia}).

@@

\section{Software implementation}

We have implemented the methods described in the previous sections though
a software written in Python language.
The code for generating the results of this work are available in
\url{https://doi.org/10.6084/m9.figshare.13604360} or
\url{https//github.com/compgeolab/eql-gradient-boosted}.
The gradient-boosted equivalent sources implementation is based on the
non-boosted sources available through the Harmonica library
\citep{harmonica2020}, part of the Fatiando a Terra project
\citep{fatiando2013}.
Another Python libraries were used:
Verde \citep{verde2018} to apply block reductions and managing coordinates,
Boule \citep{boule2020} for computing normal gravity,
Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
multidimensional datasets and numerical
computations,
Numba \citep{numba2015} for writing pre-comipled implementations and
parallelization,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures.
